The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-19 paper/main.tex
Added README.

\textit{Interview Q2: Does GitHub aim to change the way OSS is developed, or simply facilitate?}\\

\textit{Interview Q3: How is GitHub changing the way OSS is being developed?}\\

>>>>

\textit{Interview Q2: Many new Software Developers are will be starting their education/training already having experience with GitHub. How will Software Engineering as a discipline (and how it is taught) change to accodate the ideas popularized by GitHub?}\\

\textit{Interview Q3: There are many non-code artifacts being hosted on GitHub, for example, Object Management Group Specifications, Laws and Statutes, books... etc. Do you see GitHub participation expanding in the non-code areas?}\\
